Online Multiclass Linear Classification with Bandit Feedback

### 2019-02-05 draft/notions-of-linear-separability.tex
rename arxiv

\begin{definition}[Linear separability]
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:linear-separability-2}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}
\label{def:linear-sep}
\end{definition}

\begin{definition}[Strong linear separability]
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\label{def:strong-linear-sep}
\end{definition}

>>>>

\begin{definition}[Linear separability]
\label{definition:linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:linear-separability-2}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}
